Computing volume via non-linear rectangular infinitesimals

### 2019-08-14 Cav2D/article-template.tex
more progress with prismatoid section

\noindent
As we alluded to in the previous section we can calculate $V_{\mathcal{S}}$ using the double Cavalieri integral:
\begin{equation}
\iint\limits_{\!\mathcal{C}} f(x,y) dA =  \int_a^b\int_c^d f(h(x,y),s(x,y))~dx~dy,
\end{equation}
with $\mathcal{C}=\{\mathbf{c}(t),R\}$. We can, however, only evaluate the above integral if the transformation $T$ is known (see Figure ). We can find $T$ using Equation

>>>>

\noindent
As we alluded to in the previous section we can calculate $V_{\mathcal{S}}$ using the double Cavalieri integral:
\begin{equation}
\iint\limits_{\!\mathcal{C}} f(x,y) dA =  \int_a^b\int_c^d f(h(x,y),s(x,y))~dx~dy,
\end{equation}
with $\mathcal{C}=\{\mathbf{c}(t),R\}$. We can, however, only evaluate the above integral if the transformation $T$ is known (see Figure ). We can find $T$ using Equation and 
Equation. To evaluate Equation and Equation we first need to express $t$ in terms of $x_i^1$ and $y_i^1$. If we substitute $f(x,y)$ and $\mathbf{c}(t)$ into Equation we find 
the following expression for $t$:
\begin{equation}
xxx. 
\end{equation}
If we substitute $xxx$ into Equation and Equation we obtain:
\begin{equation}
yyyy 
\end{equation}
and
\begin{equation}
zzzz 
\end{equation}
If we substitute yyyy and zzzz into kkkk we obtain:

We can easily verify that the $V_{\mathcal{S}}$ we computed is correct, since S is a prismatoid. According to the prismatoid volume 
equation $V_{\mathcal{S}}=25.6$. The details of this computation is described in the caption of Figure~\ref{fig:prismatoid}. This result verifies 
the fact that
